\documentclass[a4paper,12pt]{article}

% Packages
\usepackage[margin=1in]{geometry}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{array}
\usepackage{booktabs}

\title{Demonstration of Lists, Tables, and Multi-Column Layouts}
\author{Gaurang Tyagi}
\date{\today}

\begin{document}

\maketitle

\section*{1. Lists Demonstration}

\subsection*{Bulleted List (Shopping List)}
\begin{itemize}
    \item Rice
    \item Milk
    \item Bread
    \item Eggs
    \item Vegetables
    \item Cooking Oil
\end{itemize}

\subsection*{Numbered List (Steps to Submit an Assignment)}
\begin{enumerate}
    \item Open Overleaf and create a new project.
    \item Set up the document class and required packages.
    \item Write the content using proper \LaTeX \ formatting.
    \item Compile the document to check for errors.
    \item Download and submit the final PDF.
\end{enumerate}

\section*{2. Student Grades Table}

\renewcommand{\arraystretch}{1.3} % Increase row height

\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{4}{|c|}{\textbf{Semester Grade Report}} \\ \hline
\rowcolor{gray!30}
\textbf{Name} & \textbf{Subject} & \textbf{Marks} & \textbf{Grade} \\ \hline

\multirow{2}{*}{Gaurang Tyagi} 
    & Mathematics & 92 & A+ \\ \cline{2-4}
    & Physics     & 85 & A  \\ \hline

\rowcolor{gray!15}
Manas More 
    & Chemistry   & 88 & A  \\ \hline

Ravish Ranjan
    & English     & 76 & B+ \\ \hline

Brian
    & Computer Science & 95 & A+ \\ \hline

\multicolumn{2}{|c|}{\textbf{Average Marks}} & 
\multicolumn{2}{c|}{\textbf{87.2}} \\ \hline
\end{tabular}
\end{center}

% -----------------------------
% Multi-column Section
% -----------------------------
\section*{3. Newsletter Section}

\begin{center}
    {\LARGE \textbf{Monthly Tech Newsletter}} \\
    \vspace{0.5em}
\end{center}

\begin{multicols}{2}

\subsection*{Article 1: Rise of Artificial Intelligence}

Artificial Intelligence (AI) continues to reshape industries
across the globe. From healthcare diagnostics to autonomous
vehicles, AI-powered systems are improving efficiency and
accuracy. Machine learning algorithms now process vast
amounts of data in seconds, enabling smarter decisions.

Universities are introducing AI-focused programs to prepare
students for emerging careers. Ethical concerns and data
privacy remain important discussion topics. As innovation
continues, responsible development becomes essential.

\columnbreak

\subsection*{Article 2: Importance of Cybersecurity}

With increasing digital transformation, cybersecurity has
become a top priority for organizations. Cyber threats such
as ransomware and phishing attacks are growing rapidly.
Strong encryption and multi-factor authentication are now
standard security measures.

Governments and private companies are investing heavily in
cyber defense strategies. Awareness training helps users
recognize potential threats. A proactive security approach
ensures safer digital environments for everyone.

\end{multicols}

\end{document}
